Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-06 paper.tex
Corrections and new text about SOM here and there. Please @JJ and @7ossam81 check it

In addition, in order to reduce the dimensionality of the input data
and to choose an appropriate set of variables, the Self-Organizing Map
(SOM) \cite{kohonen1998} method has been also applied. % Why? Is that
                                % one of the two forms of feature
                                % selection? What do we expect to
                                % learn from it? - JJ

@@

SOM is a type of unsupervised neural network inspired by the
topographical organisation of the sensory cortex of human brain
\cite{kohonen1998}. It maps highly dimensional data into a lower
dimensional space where similar data patterns are located in more
adjacent areas on the grid. 
It is a very useful analysis tool for visualising complex data with
high number of variables in a simple geometric plane. Therefore, it
could be used for different tasks such as feature selection and data
clustering and visualisation. %Pablo: some cite here?

@@

When the learning process is done a visual representation method like
the Unified Distance Matrix, or U-matrix for short, is used to
visualize the distances between neurons in the output space. In the
U-matrix, the distance between adjacent neurons is measured and
assigned different colors. Dark colors between neurons indicate large
distances (boundaries) while ligh colors represent similar areas
(clusters).

@@

This method is usually applied to analyse data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those
regions, or clusters, with high training sample concentration and fewer
where the samples are scarce.  
%FERGU: mencionarlo en la intro
% Which is interesting because... JJ

As far as the feature selection methods are concerned, Weka software separates the process into two parts:
%FERGU: por qué mencionamos a Weka aquí y no antes?
% Antonio - se ha mencionado, pero sí, habría que destacarlo un poco más desde la intro quizá.
\begin{itemize}
  \item Attribute evaluator: This is the method by which the feature subsets are assessed. In this work, both a correlation-based feature subset evaluation method ({\tt CfsSubsetEval}) and an adaptation of relief for attribute estimation ({\tt ReliefFAttributeEval}) evaluation method are used.

  The Correlation Feature Selection (CFS) method evaluates subsets of features/variables on the basis of the hypothesis made by Hall in \cite{Hall1998}, ``A  good  feature  subset  is  one  that  contains  features  highly  correlated  with
(predictive of) the class, yet uncorrelated with (not predictive of) each other''. This evaluator needs the numeric features to be transformed to nominal features first, by being discretised. The CFS evaluation function measures the ``merit'' of the subsets, which depend on the mean feature-class correlation, and the average feature-feature intercorrelation. In addition, the correlation is measured by three variations: the Minimum Description Length (MDL), the symmetrical uncertainty, and the ``relief''.

@@

Figure \ref{fig:componentplanes} shows the U-matrix and component
variables resulted from SOM training. The term component is used in
% really, are you reading this with the mind of someone that has no
% idea what is SOM or U-Matrix or whatever? Tell first what you are
% going to do, then tell why you are doing it, explain all the
% terminology and then show the results. You can't keep saying "I have
% done this and this is the result. You have to explain why you are
% doing it, what you are doing, how you are doing it and then how to
% interpret the results - JJ
SOM to refer to the features. %use features!!!! - JJ
 The component planes in Figure %what is a plane? Really, you don't
                                %know what's in the mind of the reader
                                %(or reviewer#3, who is a son of a
                                %bitch - JJ
\ref{fig:componentplanes} show the trend of values of the prototype
vectors of the SOM map units. These values are represented as
colours. The colorbar on the right of each component plane shows the
indication of each colour. On the other side, the U-matrix on the top
left corner shows the distances between the adjacent units. It is
important to note that high values in the matrix indicates large
distance between the units of the map. It can be noticed also that
there are more hexagons in the U-matrix than component planes since
the distances between units is also represented as hexagons. % but
                                % explain that at the beginning!
                                % Devote one or two paragraphs to tell
                                % the reader what is U-Matrix, a
                                % reference, why we are using it and
                                % how it conveys more information that
                                % a pure and simple feature selection
                                % (which we are doing anyway). If we
                                % don't, Reviewer #3 (who is,
                                % remember, a son of a bitch) will
                                % tell you to just suppress that whole
                                % section - JJ

>>>>

In addition, in order to reduce the dimensionality of the input data
and to choose an appropriate set of variables, the Self-Organizing Map
(SOM) \cite{kohonen1998} method has been also applied as a `subjective' (based on expert's opinion) feature selection technique based on the visualisation of the data as a set of 2D planes (one per feature of the dataset), and their interpretation for finding out relationships between these features.

% Why? Is that one of the two forms of feature selection? What do we expect to learn from it? - JJ 
% Antonio - explained here and below. Please check.

@@

SOM is a type of unsupervised neural network inspired by the
topographical organisation of the sensory cortex of human brain
\cite{kohonen1998}. It maps highly dimensional data into a lower
dimensional space where similar data patterns are located in more
adjacent areas on the grid. 
% It is a very useful analysis tool for visualising complex data with high number of variables in a simple geometric plane. 
%Therefore, it could be used for different tasks such as feature selection and data clustering and visualisation. %Pablo: some cite here?
This method is normally used as a data visualization tool, since it allows to project any multi-variated dataset in a two-dimensional display, so an expert can detect topological relations among its neurons and thus make inferences or find interesting relationships on the input dataset (such as clusters, for instance).

@@

Once the SOM learning process is finished, a visual representation technique, named the Unified distance matrix (U-matrix) \cite{UmatUlts}, has been applied. This method uses the obtained codevectors (vectors of variables of the problem) as data source, and generates a matrix where each component is a distance measure between two adjacent neurons. In the U-matrix, the distance between adjacent neurons is measured and assigned different colors. Different colors between neurons indicate large distances (boundaries) while similar colors represent close areas (clusters).

% Antonio - a better description of U-Matrix. ;D

@@

This method is usually applied to analyse data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those
regions, or clusters, with high training sample concentration and fewer
where the samples are scarce. U-Matrix graph, together with the projection of variables into separate planes, the so-called component planes analysis (that SOM yields), will aid an expert to identify the most relevant features on every cluster, i.e. those that can have a higher influence on the creation of that cluster.
%FERGU: mencionarlo en la intro
% Which is interesting because... JJ
% Antonio - explained. ;)

With respect to feature selection methods, the used Weka software separates the process into two parts:

\begin{itemize}
  \item Attribute evaluator: This is the method by which the feature subsets are assessed. In this work, both a correlation-based feature subset evaluation method ({\tt CfsSubsetEval}) and an adaptation of relief for attribute estimation ({\tt ReliefFAttributeEval}) evaluation method are used.

  The Correlation Feature Selection (CFS) method evaluates subsets of features/variables on the basis of the hypothesis made by Hall in \cite{Hall1998}, ``A  good  feature  subset  is  one  that  contains  features  highly  correlated  with
(predictive of) the class, yet uncorrelated with (not predictive of) each other''. This evaluator needs the numeric features to be transformed to nominal features first, by being discretized. The CFS evaluation function measures the ``merit'' of the subsets, which depend on the mean feature-class correlation, and the average feature-feature intercorrelation. In addition, the correlation is measured by three variations: the Minimum Description Length (MDL), the symmetrical uncertainty, and the ``relief''.

@@

Figure \ref{fig:componentplanes} shows the U-matrix along with the component planes analysis resulted from SOM training. The term component refers in SOM to a variable or feature of the problem.
% really, are you reading this with the mind of someone that has no
% idea what is SOM or U-Matrix or whatever? Tell first what you are
% going to do, then tell why you are doing it, explain all the
% terminology and then show the results. You can't keep saying "I have
% done this and this is the result. You have to explain why you are
% doing it, what you are doing, how you are doing it and then how to
% interpret the results - JJ
% Antonio - now it must be clearer with the new explanations given before
The component planes in Figure 
%what is a plane? Really, you don't know what's in the mind of the reader (or reviewer#3, who is a son of a bitch - JJ
% Antonio - now it should be clear. This is the accurate term for the output of SOM: component planes analysis
\ref{fig:componentplanes} show the trend of values of the prototype
vectors of the SOM map units. These values are represented as
colours. The colorbar on the right of each component plane shows the
indication of each colour. On the other side, the U-matrix on the top
left corner shows the distances between the adjacent units. It is
important to note that high values in the matrix indicates large
distance between the units of the map. It can be noticed also that
there are more hexagons in the U-matrix than component planes since
the distances between units are also represented as inter-neuron hexagons. 
                                % but
                                % explain that at the beginning!
                                % Devote one or two paragraphs to tell
                                % the reader what is U-Matrix, a
                                % reference, why we are using it and
                                % how it conveys more information that
                                % a pure and simple feature selection
                                % (which we are doing anyway). If we
                                % don't, Reviewer #3 (who is,
                                % remember, a son of a bitch) will
                                % tell you to just suppress that whole
                                % section - JJ
% Antonio - I have done it. However Ihave focused the explanation on the feature selection 'ability' of the method. ;)
